supplmental

### 2019-12-31 paper_stats.Rmd
tables

  library(sjPlot)
  library(tidyverse)
  library(broom)
  library(knitr)

@@

  data_frame(Variable       = name.1(descript),
             N              = n.miss(descript),
             "Mean SD"      = summary.1(descript),
             "Median [IQR]" = med.iqr(descript),
             "(Min, Max)"   = min.max(descript))

@@

  table_df <- full_join(means_df, difs_df, by = "Outcome") %>%
    select(Outcome, everything())

  kable(table_df)

>>>>

  library(sjPlot)
  library(tidyverse)
  library(broom)
  library(knitr)
  library(pander)

@@

  data_frame(Variable       = name.1(descript),
             N              = n.miss(descript),
             "Mean SD"      = summary.1(descript),
             "Median [IQR]" = med.iqr(descript),
             "(Min, Max)"   = min.max(descript)) %>%
  as.matrix() %>%
  kable()

@@

  full_join(means_df, difs_df, by = "Outcome") %>%
    select(Outcome, everything()) %>%
    as.matrix() %>%
    pander()
